---
title: "hw01_dataset_exploration"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset exploration

In this document I will explore a dataset in R. 

First of all, lets download an easy accessible or in-build dataset in R. Once called `data()` a new file shows you which pre-build datasets are available in the package "datasets". I decided to look at the dataset *mtcars* (Motor Trend Car Road Tests):

```{r data}
# Load data
data(mtcars)

# look at the first rows in the dataset
head(mtcars)
```

I can also look at the last couple of rows in the dataset. FOr example, I would like to look at the last 3 rows in the dataset:

```{r}
tail(mtcars, 3)
```

I wonder how many rows this dataset has:

```{r}
nrow(mtcars)
```

To find out more about the dataset I can also simply type `?mtcars` after I loaded the dataset in the console. Furthermore, I can look at the `summay`:

```{r}
summary(mtcars)
```


## Plotting data

I am also curious how easy it is to plot data.
I would like to test this on the `mtcars` dataset. 
I can for example explore the relationship between `hp` (the Gross horsepower) and `mpg` (Miles/(US) gallon.

Here fore I woudl like to inspect the specific columns first:

```{r}
hp = mtcars$hp
summary(hp)
```
```{r}
summary(mtcars$mpg)
```

Now lets plot the relationship:

```{r relationship, echo=FALSE}
plot(hp~mpg,mtcars)
```

